Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-07 writeup/gz_hubble_data.tex
Acknowledge SankeyMatic

\subsection{Selection of \ferengi{} input galaxies}

@@

\subsection{Results of $\zeta$ approach}\label{ssec:zeta_results}

@@

\section{The GZH catalog}\label{sec:results}

@@

\subsection{Example 1: Selecting bars}

@@

This paper presents the catalog release for the Galaxy Zoo: Hubble project, which uses crowdsourced visual classifications to measure galaxy morphologies. The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of low-redshift galaxies from SDSS; this is the first phase of the project with space-based images of high-redshift targets (in addition to the Galaxy Zoo: CANDELS collaboration; Simmons et al., submitted). The final sample includes classifications for 181,101~images generated from 150,771~unique galaxies. Galaxies were selected from a brightness-limited sample from multiple Legacy surveys using the Advanced Camera for Surveys on the Hubble Space Telescope, including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at relatively low redshift; these serve both as a low-redshift anchor for cosmological studies and a potential comparison for the different epochs of classification between GZH and Galaxy Zoo 2 \citep{wil13}.

The data for the GZH catalogs has been extensively tested and reduced. The dominant effect is a known bias against identifying disky and asymmetric sub-structures at either low resolution or surface brightness. This can be the result either of genuinely small or dim galaxies, or a perceived effect from observing galaxies at further distances (higher redshift). To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, the GZH project uses SDSS images of low-redshift galaxies, processes them to appear as if they were at higher redshift, and classifies them through the GZH interface in an identical fashion. The resulting change in \pfeatures{} as a function of $z$,$\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.

@@

This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and TOPCAT \citep{tay05,tay11}. Modified code from Nick~Wherry and David~Schlegel was used to create the JPG images.

>>>>

\subsection{Generating images of artifically-redshifted galaxies}

@@

\subsection{Effects of morphological debiasing}\label{ssec:zeta_results}

@@

\section{The Galaxy Zoo: Hubble catalog}\label{sec:results}

@@

\subsection{Example 1: Selecting barred galaxies}

@@

This paper presents the catalog release for the Galaxy Zoo: Hubble project, which uses crowdsourced visual classifications to measure galaxy morphologies. The first two phases of Galaxy Zoo \citep{lin11,wil13} used images of low-redshift galaxies from SDSS; this is the first result of the project with space-based images of high-redshift targets (in addition to the Galaxy Zoo: CANDELS collaboration; Simmons et al., submitted). The final sample includes classifications for 181,101~images generated from 150,771~unique galaxies. Galaxies were selected from a brightness-limited sample from multiple Legacy surveys using the Advanced Camera for Surveys on the Hubble Space Telescope, including AEGIS, GEMS, GOODS-N, GOODS-S, and COSMOS. The catalog also includes classifications for 51,861 Sloan Digital Sky Survey images in Stripe~82 at relatively low redshift; these serve both as a low-redshift anchor for cosmological studies and a potential comparison for the different epochs of classification between GZH and Galaxy Zoo 2 \citep{wil13}.

The data for the GZH catalogs has been extensively tested and reduced. The dominant effect is a known bias against identifying disky and asymmetric sub-structures at either low resolution or surface brightness. This can be the result either of genuinely small or dim galaxies, or a perceived effect from observing galaxies at further distances (higher redshift). To calibrate this \emph{without} potentially overcorrecting for the genuine morphological evolution of galaxies over cosmic time, the GZH project uses SDSS images of low-redshift galaxies, processes them to appear as if they were at higher redshift, and classifies them through the GZH interface in an identical fashion. The resulting change in \pfeatures{} as a function of $z$ and $\mu$ is applied as a multiplicative correction to the top-level vote fractions for $\sim50\%$ of the GZH galaxies.

@@

This project made heavy use of the Astropy packages in Python \citep{ast13}, the \texttt{seaborn} plotting package \citep{was15}, astroML \citep{van12}, and TOPCAT \citep{tay05,tay11}. Modified code from Nick~Wherry and David~Schlegel was used to create the JPG images. Figure~\ref{fig:sankey} was generated with \url{http://sankeymatic.com/}.
